\section{Muon reconstruction}
\label{sec:reco-muon}

Muons produced in $pp$ collisions in CMS 
are measured by reconstructing their trajectories to form ``tracks''.
Muon tracks are reconstructed independently 
by the inner tracker and by the muon subsystem, and those two
independent measurements are then combined.
The tracks reconstructed by the inner tracker system alone 
are called ``tracker tracks''.
The tracks reconstructed by the muon subsystem alone are called
``standalone muon tracks''.
There are two reconstruction methods using these objects 
as inputs: an outside-in method, which produces``global muons'',
and an inside-out method, which produces ``tracker muons''.

The global muon reconstruction method begins with the
collection of all standalone muons from the muon subsystem.
For each standalone muon, the algorithm searches for a matching
tracker track.  If a matching tracker track is found, 
a global muon track is created and refit
using all of the hits from both the standalone muon and the 
tracker track.  For muons with large \pt, the global muon 
fit can improve the muon momentum resolution over a tracker-only fit.

The tracker muon reconstruction method begins with the 
collection of all tracker tracks with $\pt>0.5$~\GeV and 
$p>2.5$~\GeV.  For each of these tracker tracks, the algorithm
searches for a matching standalone muon track, taking expected
energy loss and uncertainty from multiple scattering into account.
If one muon segment (a short track stub made of DT or CSC hits) 
matches the position predicted by the tracker track, 
the tracker track qualifies as a tracker muon track.  The
tracker muon reconstruction method is more efficient for low
momentum ($p < 5$~\GeV) muons, since it requires only one muon segment in the 
muon system, while the global muon method generally only
becomes efficient with two or more segments.

A third category of muons is added as a catch-all.  ``Standalone muons'' 
account for only 1\% of muons from collisions, and they consist of 
standalone muon tracks that are rejected by both the global muon 
and tracker muon reconstruction methods.  These muons are uncommon,
because the tracker and global muon reconstruction methods have such
a high efficiency.  They also have a non-negligable fake rate 
from cosmic muons \cite{muon-1}.
