\chapter{Monte Carlo Reweightings}
\label{app:reweightings}

An overview of the reweightings being applied to the MC samples is
shown in \cref{tb:reweightings}. The reweightings that are centrally
provided to the \dzero{} collaborators by the \verb=VJets= group are
indicated with ``\verb=VJets=''. The \verb=VJets= reweightings are
documented in the references provided in the text.
The other reweightings are specific to this search.
The Z-\pt{} and W-\pt{} reweightings are described in
\cref{sec:reweightings}.

The instantaneous luminosity \instLumi{} and the beamspot $z$-position
reweightings are applied to correct potential differeces between the
distributions observed in data and MC for these two quantities. The
distributions for \instLumi{} and for the the beamspot $z$-position
are determined in MC by the data events used for the zero-bias
overlay. Differences in the instantaneous luminosity profile can cause
data-MC discrepancies in the calorimeter noise and in the tracking
efficiency. Differences in the beamspot $z$-position can cause data-MC
discrepancies in the tracking acceptance.

For the diboson WW sample, a \dphi{\ell}{\ell} reweighting is applied
in addition to the WW \pt{} reweighting discussed in
\cref{sec:reweightings}. The \dphi{\ell}{\ell} reweightings accounts
for the fact that the \pythia{}-generated samples include the
$\Pquark{}\Pquark{}\to\PW\PW$ contribution, but not the
$\Pgluon{}\Pgluon{}\to\PW\PW$ contribution.

All the reweightings computed from data are derived in the same way.
The histograms containing the distribution of the variables for which
the reweighting is being computed are rebinned. The bins have variable
width, and their width is chosen so that the number of events in each
bin is sufficient to avoid large statistical fluctuations. The
bin-by-bin ratio of data/MC is then computed, and the resulting
histogram is modified by a smoothing algorithm.

The reweighting of the jet $\eta$ and $\dR{j_1}{j_2}$ distributions is
attributed to a limitation of the \alpgen{} generator. The jet
reweightings are applied to the \zGam{} samples only.

\begin{center}
\begin{tabular}{ l  c  c c }
  \toprule
  Reweighting                & Samples               & Notes  \\
  \midrule
  Z-\pt{} inclusive          & \zGamJets{}           &   \verb=VJets= \\
  Z-\pt{} N-jet dep.         & \zGamJets{}           &   \verb=VJets= \\
  W-\pt{} N-jet dep.         & \wJets{}              &   \verb=VJets= \\
  Instantaneous luminosity   & All                   &   \verb=VJets= \\
  Beamspot $z$-position      & All                   &   \verb=VJets= \\
  WW $p_T$                   & Diboson WW            &   \mcatnlo{} \\
  WW $\Delta\phi$            & Diboson WW            &   \sherpa{} \\
  H $p_T$                    & \ggHww{}              &   \hqt{} \\
  Detector $\eta$            & All, inclusive        &   From data\\
  Unclustered energy         & All, N-jet sep.       &   From data\\
  Jet1 $\eta$                & \zGam{}, 1-jet and 2-jet  &   From data\\
  Jet2 $\eta$                & \zGam{}, 2-jet            &   From data\\
  $\dR{j_1}{j_2}$            & \zGam{}, 2-jet            &   From data\\
\bottomrule
\end{tabular}
\label{tb:reweightings}
\end{center}
% The \dphi{\ell}{\ell} distributions of the production processes
%   $qq\to{}WW$ and $gg\to{}WW$ differ significantly.  Since this
%   difference is not considered by Pythia an appropriate reweighting at
%   parton level has been derived and applied to the $WW$ background
%   sample. The uncertainty due to the $gg\to{}WW$ reweighting are
%   calculated by not applying the reweighing and symmetrizing 30\% of
%   the resulting uncertainty.  The uncertainty is found to be at the
%   order of 1\%.\checkThis{rephrase, move some stuff to
%     \ref{sec:reweightings}}
