\section{Event filters}
\label{sec:event-filters}

All events in this analysis (both \eejj~and \enujj~channels)
are required to pass the event filters described in this section.  These filters
are designed to reject beam background, detector electronics
noise, and other detector artifacts.  These filters are placed on both
data and MC events, unless otherwise indicated.

\begin{itemize}
  \item {\bf BPTX coincidence:} The beam pickup timing for the experiments (BPTX)
    \nomenclature{BPTX}{Beam pickup timing for the experiments} is a beam pickup
    device designed to provide the experiments with precise information on the bunch structure
    and the timing of the LHC beam. Two are installed for CMS: 175 m in either direction of the IP.
    A coincidence of signals from both BPTX detectors (indicating a $pp$ crossing at the IP)
    is required for all data events in this analysis.  BPTX coincidence is not required 
    for MC events.
  \item {\bf Primary vertex requirement:} At least one ``good'' primary vertex is 
    required to be reconstructed in each event.  A good primary vertex is defined
    to be a primary vertex reconstructed with more than four degrees of freedom
    (see Section \ref{sec:reco-vtx}) and to have position with $|z| < 24$ cm and 
    $\rho < 2$ cm.
  \item {\bf Beam scraping filter:} This filter requires a fraction of {\it highPurity}
    tracks (see Section \ref{sec:reco-track}) to be great than 25\% in events with more than
    10 tracks.  This requirement removes a rare beam-induced background known as ``beam scraping'',
    which arises from interactions between the beam and both residual gas particles 
    and beam collimators.  These interactions can produces showers of secondary particles, which
    the tracker registers as isotropic noise \cite{cms-jinst}.
  \item {\bf Beam halo filter:} This filter takes information from the endcap muon system
    (see the CSCs in Section \ref{sec:muon}) to reject a beam-induced background known 
    as ``beam halo'', which manifests as charged particles travelling parallel to the beam
    at a large radius.  Beam halo can be severely detrimental to \met~measurements.
  \item {\bf HBHE noise filter:} This filter is designed to reject 
    noise from the HB and HE readout electronics, which can be mistakenly reconstructed
    as hadronic energy deposits.  
\end{itemize}
