\section{$W/Z+$jets background}
\label{sec:vjets}

Once the QCD multijets and \ttbar~background estimates have been determined,
the \zjets~and \wjets~contributions may be extracted.
In both the \eejj~and \enujj~channels, the \zjets~and \wjets~contributions
to the total background estimates are obtained using MC that has
been rescaled within control regions.
  
\subsection{\zjets~background in the \eejj~channel} 
\label{sec:eejjZjetsBkg}

The \zjets~selection efficiency in the \eejj~analysis is derived from MC.
The \zjets~MC sample normalization is obtained by comparing 
data and simulation as described below.

After applying the \eejj~preselection and requiring that the invariant mass 
of the di-electron pair is close to the \PZz~peak 
($70<\mbox{\mee}<110$~\GeV), the sample is dominated by \zjets~events 
with a contamination from other SM processes of \ContaminationAtZpeak, estimated from MC, 
mostly coming from \ttbar~and diboson events.
At this stage of the selection, the data are compared to the background predictions
and an overall good agreement is found in the shape of the 
distributions of all the observables employed in the final selection.
A data/MC rescaling factor is then computed for the \zjets~background, using Equation \ref{eqn:zjetsRescale}:
\begin{equation}
  \mathcal{R}_{\mbox{\PZz}} = \frac{\mbox{N}_{\mbox{data}} - ( \mbox{N}_{\mbox{Others}} + \mbox{N}_{\mbox{QCD}} )}{\mbox{N}_{\mbox{\PZz}}} = \mbox{\rescaleFactorZSherpa}
  \label{eqn:zjetsRescale}
\end{equation}
where $\mbox{N}_{\mbox{data}} $, $\mbox{N}_{\mbox{Others}}$, $\mbox{N}_{\mbox{\PZz}}$, 
and $\mbox{N}_{\mbox{QCD}}$ are, respectively, the number of events in data, the 
number of events predicted by other MC samples (including \ttbar, \wjets, 
diboson, and others), the number of events predicted by the \zjets~MC sample before rescaling, 
and the number of events predicted by the QCD multijet events obtained with the method described in Section~\ref{sec:qcd}.
This factor is already included in the \zjets~MC predictions for \eejj~channel.
The systematic uncertainty on the rescaling factor comes from the systematic uncertainty on the 
data driven QCD multijet and \ttbar~estimates.

\subsection{\wjets~background in the \enujj~channel} 
\label{sec:enujjWjetsBkg}

The \wjets~selection efficiency in the \enujj~analysis is derived from MC.
The \wjets~MC sample normalization is obtained by comparing 
data and simulation, simultaneously with the \ttbar~background, 
as described in Section~\ref{sec:enujjTTbarWJetsBkg}.

