\begin{singlespace} % acknowledgments don't need to be double-spaced
\addcontentsline{toc}{chapter}{Acknowledgments}
\chapter*{Acknowledgments}

The work described in this thesis is a product 
of the help and support that I have received from many
people over many years.

First among these is my advisor, Christopher Tully, whom I 
would like to thank for taking me onto his team.
Chris is one of the most knowledgable and talented physicists
I have ever met.  His support and insight have been invaluable.

I would also like to thank the members of the lepton-jet
exotica working group at CMS, who reviewed this analysis and helped
move it towards publication.  The conveners have been extremely
helpful and informative, and my fellow analysts have been the 
best colleagues I could have asked for.  This is especially true
of Paolo Rumerio and Francesco Santanastasio, who have been like
second advisors to me. 
Special thanks is also due to Jim Hirschauer, whose careful
review and watchful eye were essential for getting this analysis published.
All three are teachers, leaders, and scientists of the highest caliber.

This thesis and many other analyses at CMS would have been unthinkable without
a hadronic calorimeter and a team of experts to keep it
running.  CMS is a successful experiment thanks to the hard work of people like
Pawel de Barbaro, Phil Dudero, Yossof Eshaq, Richard Kellogg, Ted Laird,
Phil Lawson,  Dragoslav Lazic, Jeremy Mans, German Martinez, 
Sudan Paramesvaran, Halil Saka, Jared Sturdy, Taylan Yetkin, 
and too many others to name.  I would like to thank them for their work and for teaching me
so much about the detector.

My colleagues in the Princeton CMS office shared a long and difficult road
with me, and it is impossible to imagine life at CERN without them.
It has been a privilege to work alongside Davide Gerbaudo, 
Phil Hebda, Adam Hunt, Paul Lujan, Tatiana Medvedeva, Michael Mooney, 
Xiaohang Quan, and Andrzej Zuranski.  

I have been blessed to have studied under too many excellent teachers to list here.
David Dannels showed me how to write my first line of code and how to 
write my first physics lab report.  His presence in the classroom is sorely missed.
Mark Vondracek was the first high energy physicist I ever met, and the day
he showed me a picture of the CDF detector changed my life.
Ivan Furic and Young-Kee Kim were kind enough
to welcome me into the HEP group at the University of Chicago
and to guide me to my first published result.
My sincere thanks go to all of them, and the 
debt I owe them can never be fully repaid.

My family has been a source of unwavering support, and no
words in these acknowledgements can adequately thank them.  
My mother and father, Carrie Jeffers and John Berry,
are both models of love and 
compassion.  They are my role models in everything I do.
Tom Berry and Jim Berry, are smart, driven, and kind
in addition to being the best brothers I could imagine.
Our time together is too rare and always too short.

Finally, I want to thank my wife and best friend, Colette Berry n{\'e}e Borden.
I came to Europe to search for new physics, and instead I found
someone who means more to me than any kind of physics ever could.
She has worked tirelessly to forge her own career while
simultaneously supporting me through mine, and 
this thesis would not have been possible without her.
Thank you for everything.

\end{singlespace}
\newpage
\lhead{\leftmark} % change header format back
